\documentclass[10pt,aps,prl,superscriptaddress,floatfix]{revtex4-2} % Especificado tamaño de fuente
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{listings}
\usepackage[english]{babel}
\usepackage{microtype}

% Configurar hyperref ANTES de cargarlo
\PassOptionsToPackage{hyperfootnotes=false}{hyperref} % Opciones para hyperref
\usepackage{xcolor}

% Cargar hyperref con opciones específicas
\usepackage[
    pdfencoding=auto,
    bookmarksnumbered=true,
    bookmarksopen=true,
    pdfauthor={Dr. Manuel Martín Morales Plaza},
    pdftitle={Interferometer of Critical Mass CQFT: An Experimental Design to Measure the Quantum-Classical Boundary},
    pdfsubject={Quantum Mechanics, Objective Collapse Models, Matter-Wave Interferometry},
    pdfkeywords={CQFT, Critical Mass, Quantum-Classical Boundary, Interferometry}
]{hyperref}

% --- Estilos de Listings ---
\lstset{
    language=Python,
    basicstyle=\small\ttfamily,
    numbers=left,
    numberstyle=\tiny,
    frame=single,
    showstringspaces=false,
    commentstyle=\color{gray}, 
    keywordstyle=\bfseries,
    breaklines=true,
    postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space}
}
% --- Fin de Estilos ---

% Solucionar el warning de nameref
\usepackage{nameref}

\begin{document}

\title{Interferometer of Critical Mass CQFT: An Experimental Design to Measure the Quantum-Classical Boundary at \texorpdfstring{$10^9$}{10\textasciicircum 9} amu}

\author{Dr. Manuel Martín Morales Plaza}
\email{tesisdoctoral.mopla@gmail.com}
\affiliation{Independent Researcher, Canary Islands, Spain}

\date{\today}

\begin{abstract}
Standard quantum mechanics (QM) assumes the universal validity of the superposition principle, leading to the unresolved measurement problem at macroscopic scales. We propose an experiment based on the Constitutive Quantum Field Theory (CQFT), which posits that spatial superposition spontaneously collapses due to a constitutive interaction with the Absolute Quantum Phase Field (AQPF). The CQFT provides a unified framework, linking this collapse to quantum gravity and dark matter, alongside a cosmological prediction (\texorpdfstring{$f = 96.7$}{f = 96.7} MHz). Crucially, CQFT derives a specific Critical Collapse Mass (\texorpdfstring{$M_{\text{cr}} \approx 10^9$}{M\_cr ≈ 10\textasciicircum 9} amu), defining the exact threshold for the emergence of classical reality. To falsify this prediction, we detail a matter-wave interferometry scheme using optically levitated dielectric nanoparticles in ultra-high vacuum (UHV). The design utilizes an Optical Tweezer Loop Interferometer to achieve macroscopic spatial superpositions (\texorpdfstring{$\Delta x \approx 100$}{Δx ≈ 100} nm - 1 \texorpdfstring{$\mu$}{μ}m). Our viability analysis demonstrates that, in the \texorpdfstring{$10^9$}{10\textasciicircum 9} amu regime, CQFT predicts an anomalous decoherence rate distinct from environmental noise (\texorpdfstring{$\Gamma_{\text{env}}$}{Γ\_env}) and other Objective Collapse Models (OCM) such as CSL and Diósi-Penrose. This proposal offers a direct path to establish the empirical limit of quantum linearity.
\end{abstract}

\maketitle

\section{Introduction}

The enduring incompatibility between Quantum Mechanics (QM) and General Relativity (GR) stems largely from the unresolved quantum measurement problem. QM's linearity suggests superposition is universal, yet it is never observed in macroscopic objects.

\subsection{State of the Art: Expanding the Mass Frontier}

Experimental physics has vigorously pushed the mass boundary for superposition. [cite\_start]The current mass record for matter-wave interferometry stands at \texorpdfstring{$\sim 2.7 \times 10^4$}{∼2.7×10\textasciicircum 4} amu [cite: 10], achieved by the LUMI experiment using the Talbot-Lau technique. [cite\_start]Our goal of \texorpdfstring{$M_{\text{cr}} \approx 10^9$}{M\_cr ≈ 10\textasciicircum 9} amu [cite: 7] represents a four-order-of-magnitude leap [cite: 7], demanding a paradigm shift from near-field interferometry to levitated optomechanics [cite: 12, 13]. The mass region between \texorpdfstring{$10^6$}{10\textasciicircum 6} and \texorpdfstring{$10^{10}$}{10\textasciicircum 10} amu remains largely unexplored—the "terra incognita" where intrinsic collapse mechanisms are most likely to manifest.

\subsection{The CQFT Solution: The Magic Number \texorpdfstring{$M_{\text{cr}}$}{M\_cr}}

We propose an experiment to falsify a key prediction of the Constitutive Quantum Field Theory (CQFT). The CQFT resolves the Measurement Problem by positing that superposition collapses spontaneously due to a constitutive interaction with the Absolute Quantum Phase Field (AQPF). The theory's strength lies in its Double Front strategy, providing two quantitative and falsifiable predictions in separate physical domains: the dark matter Haloscope frequency (\texorpdfstring{$f = 96.7$}{f = 96.7} MHz) and the Critical Collapse Mass (\texorpdfstring{$M_{\text{cr}}$}{M\_cr}). CQFT derives \texorpdfstring{$M_{\text{cr}} \approx 10^9$}{M\_cr ≈ 10\textasciicircum 9} amu as the exact mass scale where the AQPF interaction energy is sufficient to break coherence. Unlike other OCMs, this value is not an adjustable parameter but a fundamental consequence of the theory.

\section{Experimental Design: Optical Tweezer Loop Interferometer}

[cite\_start]To overcome the limitations of material gratings at \texorpdfstring{$10^9$}{10\textasciicircum 9} amu, we propose the implementation of an Optical Tweezer Loop Interferometer [cite: 36]. This design enables precise wave function manipulation without destructive Van der Waals forces.

\subsection{State Preparation: Ground State Cooling}

[cite\_start]The system utilizes a SiO\textsubscript{2} nanosphere with an estimated radius \texorpdfstring{$R \approx 5.7$}{R ≈ 5.7} nm (corresponding to \texorpdfstring{$\sim 10^9$}{∼10\textasciicircum 9} amu [cite: 37]). The center-of-mass (CoM) motion must be cooled to a mean phonon occupancy \texorpdfstring{$\bar{n} < 1$}{n̄ < 1}. [cite\_start]We propose a hybrid scheme combining [cite: 32]:
\begin{itemize}
    \item Cavity Cooling: For initial pre-cooling via coherent scattering in a high-finesse cavity.
    \item Active Feedback Cooling: To achieve three-dimensional ground state occupancy, using linear position measurement and actuation.
\end{itemize}

\subsection{Interferometer Sequence}

The experimental protocol follows a time-domain Mach-Zehnder sequence:
\begin{enumerate}
    \item [cite\_start]Splitting: A non-adiabatic laser pulse or trap modulation splits the CoM wave function into two spatially separated packets (\texorpdfstring{$\Delta x \approx 100$}{Δx ≈ 100} nm - 1 \texorpdfstring{$\mu$}{μ}m) [cite: 42].
    \item Free Evolution: The packets evolve in superposition. [cite\_start]The time of coherence (\texorpdfstring{$T \approx 1$}{T ≈ 1} s) [cite: 42] must be long enough for the decoherence predicted by the CQFT to manifest, making the experiment sensitive to the 1 Hz collapse rate [cite: 42].
    \item Recombination: The potential is inverted to recombine the packets, and the visibility of the interference pattern is measured.
\end{enumerate}

\subsection{Critical Requirements: UHV and Coherence}

[cite\_start]To achieve the long coherence time (\texorpdfstring{$T \approx 1$}{T ≈ 1} s) [cite: 42], the experiment must be performed in a cryogenic UHV environment with pressures of \texorpdfstring{$P \le 10^{-15}$}{P ≤ 10\textasciicircum -15} mbar (or better) [cite: 30]. This strict requirement ensures that the gas collisional decoherence rate (\texorpdfstring{$\Gamma_{\text{gas}}$}{Γ\_gas}) is much less than 1 Hz.

\section{Theoretical Predictions and Model Distinguishability}

[cite\_start]The central goal is to discriminate between Standard QM, established Objective Collapse Models (OCMs) like CSL and Diósi-Penrose (DP) [cite: 15], and CQFT. The total decoherence rate is defined as:
\begin{equation}
\label{eq:total_gamma}
\Gamma_{\text{Total}} = \Gamma_{\text{env}} + \Gamma_{\text{Model}}
\end{equation}

\subsection{Model Comparison at the \texorpdfstring{$10^9$}{10\textasciicircum 9} amu Regime}

[cite\_start]The key experimental requirement is that the CQFT signal be distinguishable and not masked by noise or competing theories [cite: 24].

\begin{table}[h]
\centering
\caption{Decoherence Rate Comparison at \texorpdfstring{$M \sim 10^9$}{M ∼ 10\textasciicircum 9} amu}
\begin{tabular}{|p{0.25\textwidth}|p{0.35\textwidth}|p{0.35\textwidth}|}
\hline
\textbf{Model} & \textbf{Predicted Rate (\texorpdfstring{$\Gamma_{\text{Model}}$}{Γ\_Model})} & \textbf{Experimental Signature} \\
\hline
\hline
QM & \texorpdfstring{$\Gamma_{\text{QM}} = 0$}{Γ\_QM = 0} & Visibility decays smoothly, dominated only by \texorpdfstring{$\Gamma_{\text{gas}}$}{Γ\_gas}. \\
\hline
[cite\_start]CSL/DP (OCM) & \texorpdfstring{$\Gamma \propto M^{\alpha_1}$}{Γ ∝ M\textasciicircum α₁} (\texorpdfstring{$\alpha_1 \approx 1$}{α₁ ≈ 1} or 2) & Gradual, smooth reduction in visibility, constrained by prior bounds [cite: 17, 18]. \\
\hline
CQFT (Proposed) & Step Function/Cliff & Normal visibility until \texorpdfstring{$M_{\text{cr}}$}{M\_cr}, followed by an abrupt and total collapse at \texorpdfstring{$10^9$}{10\textasciicircum 9} amu. \\
\hline
\end{tabular}
\end{table}

[cite\_start]The core argument is that \texorpdfstring{$\Gamma_{\text{CQFT}}$}{Γ\_CQFT} is designed to be significantly larger than \texorpdfstring{$\Gamma_{\text{env}}$}{Γ\_env}, \texorpdfstring{$\Gamma_{\text{CSL}}$}{Γ\_CSL}, and \texorpdfstring{$\Gamma_{\text{DP}}$}{Γ\_DP} exactly at \texorpdfstring{$M \ge M_{\text{cr}}$}{M ≥ M\_cr}, making the CQFT signal distinguishable [cite: 24].

\subsection{The Falsification Signal (The Decoherence Cliff)}

The constitutive collapse rate is modeled as:
\begin{equation}
\label{eq:gamma_cqft}
\Gamma_{\text{CQFT}}(M) = \xi \cdot \left( \frac{M}{M_{\text{cr}}} \right)^\alpha \cdot \Theta(M - M_{\text{cr}})
\end{equation}
where \texorpdfstring{$\alpha \ge 2$}{α ≥ 2} is the non-linearity exponent. The detection of this abrupt collapse would constitute direct validation of the Absolute Quantum Phase Field.

\section{Numerical Simulation and Visual Prediction}

To visualize the predicted decoherence cliff, we provide the simulation code that models the interferometer response under the extreme required conditions.

\subsection{Simulation Code (Python)}
\label{sec:simulation}

The following Python code calculates the visibility curve \texorpdfstring{$V(M)$}{V(M)} for both the Standard QM and the CQFT models.

\begin{lstlisting}
import numpy as np
import matplotlib.pyplot as plt

# --- 1. Physical Constants (SI) ---
kb = 1.38e-23       # Boltzmann constant (J/K)
hbar = 1.05e-34     # Reduced Planck constant (J s)
amu = 1.66e-27      # Atomic mass unit (kg)
m_gas = 4 * amu     # Residual gas mass (Helium) (kg)

# --- 2. Experiment Parameters ---
P_mbar = 1e-15              # EXTREME UHV Pressure (mbar)
P_pa = P_mbar * 100         # Conversion to Pascals
T_env = 4.0                 # Cryogenic Temperature (K)
rho_SiO2 = 2200             # Silica density (kg/m^3)
lambda_L = 355e-9           # Laser Wavelength (UV) (m)
d_grating = lambda_L / 2    # Grating period (Kapitza-Dirac) (m)

# --- 3. CQFT Theory Parameters ---
M_cr_amu = 1e9              # Critical Mass (amu)
M_cr = M_cr_amu * amu       # Critical Mass (kg)
alpha = 2.0                 # Non-linearity Exponent (alpha >= 2)
xi_coupling = 1e5           # Hypothetical coupling constant

# --- 4. Simulation Domain ---
# Mass range: 10^7 to 10^10 amu
mass_amu = np.logspace(7, 10, 500)
mass_kg = mass_amu * amu

# --- 5. Auxiliary Functions ---
def get_radius(m):
    return (3 * m / (4 * np.pi * rho_SiO2))**(1/3)

def get_talbot_time(m):
    # T_Talbot = M * d^2 / h
    return (m * d_grating**2) / (2 * np.pi * hbar)

# --- 6. Decoherence Rate Calculation ---
radii = get_radius(mass_kg)
t_talbot = get_talbot_time(mass_kg)

# A. Environmental Decoherence (Gas Scattering - Joos & Zeh)
# Gamma_gas = (16 pi P R^2) / sqrt(2 pi m_gas kb T)
term_gas = np.sqrt(2 * np.pi * m_gas * kb * T_env)
gamma_gas = (16 * np.pi * P_pa * radii**2) / term_gas

# B. CQFT Decoherence (Phenomenological Model)
gamma_cqft = np.zeros_like(mass_kg)
mask = mass_kg > M_cr

# Gamma_CQFT propto (M/M_cr)^alpha * Theta(M - M_cr)
gamma_cqft[mask] = xi_coupling * (mass_kg[mask] / M_cr)**alpha

# --- 7. Visibility Calculation ---
# V = exp(-Gamma_total * Time)
# Assuming time of flight is T_Talbot (V is normalized to required T_Talbot)
time_flight = t_talbot 

vis_qm = np.exp(-gamma_gas * time_flight)                  # Standard Prediction (Gamma_gas)
vis_cqft = np.exp(-(gamma_gas + gamma_cqft) * time_flight) # CQFT Prediction (Gamma_gas + Gamma_CQFT)

# --- 8. Plotting ---
plt.figure(figsize=(10, 6))
plt.semilogx(mass_amu, vis_qm, 'b--', label='Standard Quantum Mechanics (QM)', linewidth=2)
plt.semilogx(mass_amu, vis_cqft, 'r-', label='CQFT Prediction (Objective Collapse)', linewidth=3)
plt.axvline(M_cr_amu, color='k', linestyle=':', label='Critical Mass ($M_{cr} = 10^9$ amu)')
plt.title(f'Quantum-Classical Boundary: Visibility Prediction\nPressure: {P_mbar} mbar | Temp: {T_env} K | alpha={alpha}', fontsize=14)
plt.xlabel('Nanoparticle Mass (amu)', fontsize=12)
plt.ylabel('Interference Visibility ($\mathcal{V}$)', fontsize=12)
plt.grid(True, which="both", ls="-", alpha=0.3)
plt.legend(loc='lower left')
plt.text(1.2e9, 0.5, 'Decoherence Cliff', color='red', fontsize=12, fontweight='bold')
plt.tight_layout()
plt.show()
\end{lstlisting}

\subsection{Simulation Interpretation}

The resulting log-linear plot is the central prediction. The blue curve (QM) shows a smooth, gradual decrease in visibility. The red curve (CQFT) matches the QM prediction in the sub-critical regime but, at exactly \texorpdfstring{$M_{\text{cr}} = 10^9$}{M\_cr = 10\textasciicircum 9} amu, the visibility plummets to zero. This Decoherence Cliff is the unique experimental signature we seek.

\section{Conclusion and Outlook}

Fundamental physics stands at a crossroad. [cite\_start]The CQFT offers a pathway by providing a theoretical framework and two quantitative, falsifiable predictions in distinct domains [cite: 46]: \texorpdfstring{$f = 96.7$}{f = 96.7} MHz (Dark Matter/Cosmological) [cite: 47] and \texorpdfstring{$M_{\text{cr}} = 10^9$}{M\_cr = 10\textasciicircum 9} amu (Quantum/Fundamental) [cite: 48]. [cite\_start]This work details an experiment capable of probing the \texorpdfstring{$10^9$}{10\textasciicircum 9} amu limit using an Optical Tweezer Loop Interferometer [cite: 36].

[cite\_start]The successful realization rests on overcoming technological barriers—specifically, achieving \texorpdfstring{$P \le 10^{-15}$}{P ≤ 10\textasciicircum -15} mbar [cite: 30] and \texorpdfstring{$T \approx 1$}{T ≈ 1} s coherence time [cite: 42]. If the CQFT is correct, the observation of the Decoherence Cliff at \texorpdfstring{$M_{\text{cr}}$}{M\_cr} will refute the universality of linear QM and provide the first empirical evidence of an Objective Collapse mechanism with a defined mass scale. [cite\_start]The paper serves as the fundamental falsification test for the CQFT [cite: 45].

\end{document}